Ecuador plant species BIEN data

### 2022-11-28 code/L0/L0_Ecuador_plants_BIEN.Rmd
updated data pulls from BIEN to include all taxonomy, observation type and colleciton info

```{r}
# occurrence data
Ecuador_BIEN_occ <- BIEN_occurrence_country("Ecuador")
# species list
Ecuador_BIEN_species_list <- BIEN_list_country(country = "Ecuador")
# trait data
Ecuador_BIEN_traits <- BIEN_trait_country("Ecuador")
```

## Data summary
```{r}
summary(Ecuador_BIEN_occ)
na_summary(Ecuador_BIEN_occ, exclude_cols = c("date_collected"))
```

@@

### using DataExplorer package
```{r}
plot_str(Ecuador_BIEN_occ)
introduce(Ecuador_BIEN_occ)
plot_intro(Ecuador_BIEN_occ)
plot_missing(Ecuador_BIEN_occ)
plot_bar(Ecuador_BIEN_occ)
```

```{r}
plot_str(Ecuador_BIEN_species_list)
introduce(Ecuador_BIEN_species_list)
plot_intro(Ecuador_BIEN_species_list)
plot_missing(Ecuador_BIEN_species_list)
plot_bar(Ecuador_BIEN_species_list)
```

>>>>

```{r}
# occurrence data
Ecuador_BIEN_occ <- BIEN_occurrence_country("Ecuador", all.taxonomy = TRUE, observation.type = TRUE, collection.info = TRUE)
# species list
Ecuador_BIEN_species_list <- BIEN_list_country(country = "Ecuador")
# trait data
Ecuador_BIEN_traits <- BIEN_trait_country("Ecuador", all.taxonomy = TRUE)
```

## Data summary
```{r}
summary(Ecuador_BIEN_occ)
na_summary(Ecuador_BIEN_occ, exclude_cols = c("date_collected", "date_identified"))
```

@@

### using DataExplorer package
```{r}
plot_str(Ecuador_BIEN_occ)
introduce(Ecuador_BIEN_occ)
plot_intro(Ecuador_BIEN_occ)
#plot_missing(Ecuador_BIEN_occ)
#plot_bar(Ecuador_BIEN_occ)
```

```{r}
plot_str(Ecuador_BIEN_species_list)
introduce(Ecuador_BIEN_species_list)
plot_intro(Ecuador_BIEN_species_list)
```
